Hybrid platforms and bargaining

### 2023-06-11 src/presentation/io_day.qmd
Remove weighing

::: {.incremental}
 - **Hybrid platform markets**<br>
 @anderson2021hybrid, @gutierrez2021welfare, @hagiu2022should
 - Similarly structured markets
   - Private labels in retail [@steiner2004nature]
   - Vertical integration [@hart1990vertical; @de2005vertical; @montez2007downstream]
 - Cooperative games in IO<br>
 @hart1990property, @levy1997individual, @inderst2003bargaining, @montez2007downstream

@@

::: {.fragment}
 - Platform gets $$ \pi_P(N_P, N_F) = \int_0^1 w(s) f(N_P, sN_F) \mathrm{d}s $$
 - Fringe gets the rest
:::
::: {.fragment}
 - Based on the Shapley-value 
   - Bargaining interpretation [e.g. @hart1996bargaining; @gul1989bargaining]
   - Precedents in the IO literature [e.g. @hart1990property; @montez2007downstream]
 - $w(s)$ is a weighting function with $\int_0^1 w(s) \mathrm{d}s = 1$
   - Related to the weighted value for a certain class of functions
:::

@@

::: {.incremental}
 - Free entry equilibrium: fringe firms make zero net profits
   $$ \pi_F(N_P, N_F^*) = I_F N_F^* $$
 - In order to guarantee uniqueness, let us assume
   $$
   \scriptsize
   \begin{gather*}
       f'_{n_F} (N_P, N_F) < \int_0^1 s w(s) f'_{n_F} (N_P, s N_F) \mathrm{d}s \\
       \text{or} \\
       f''_{n_F} (N_P, N_F) < \int_0^1 s^2 w(s) f''_{n_F} (N_P, s N_F) \mathrm{d}s.
   \end{gather*}
   $$
     - Holds for certain interesting cases, such as the example application
:::

@@

:::
::: {.fragment fragment-index=4}
 - And sometimes total profits, too
 $$
 \begin{gather*}
   g(\alpha N_P + \beta N_F), \\
   g'' < 0, w(s) \equiv 1
 \end{gather*}
 $$
 $$
 \implies \frac{\partial N_F^*}{\partial N_P} < -\frac{\alpha}{\beta}
 $$
:::

>>>>

::: {.incremental}
 - Hybrid platform markets<br>
 **@anderson2021hybrid**, @gutierrez2021welfare, @hagiu2022should
 - Similarly structured markets
   - Private labels in retail [@steiner2004nature]
   - Vertical integration [@hart1990vertical; @de2005vertical; @montez2007downstream]
 - Cooperative games in IO<br>
 @hart1990property, **@levy1997individual**, @inderst2003bargaining, **@montez2007downstream**

@@

::: {.fragment}
 - Players get their Shapley-values 
   - Bargaining interpretation [e.g. @hart1996bargaining; @gul1989bargaining]
   - Precedents in the IO literature [e.g. @hart1990property; @montez2007downstream]
:::
::: {.fragment}
 - Platform gets $$ \pi_P(N_P, N_F) = \int_0^1f(N_P, sN_F) \mathrm{d}s $$
 - Fringe gets the rest
:::
::: {.fragment}
 - Can be extended with weighting (innate bargaining power)
:::

@@

::: {.incremental}
 - Free entry equilibrium: fringe firms make zero net profits
   $$ \pi_F(N_P, N_F^*) = I_F N_F^* $$
 - In order to guarantee uniqueness, let us assume
   $$
   \scriptsize
   \begin{gather*}
       f'_{n_F} (N_P, N_F) < \int_0^1 s f'_{n_F} (N_P, s N_F) \mathrm{d}s \\
       \text{or} \\
       f''_{n_F} (N_P, N_F) < \int_0^1 s^2 f''_{n_F} (N_P, s N_F) \mathrm{d}s.
   \end{gather*}
   $$
     - Holds for certain interesting cases, such as the example application
:::

@@

:::
::: {.fragment fragment-index=4}
 - And sometimes total profits, too
 $$
 \begin{gather*}
   g(\alpha N_P + \beta N_F), g'' < 0
 \end{gather*}
 $$
 $$
 \implies \frac{\partial N_F^*}{\partial N_P} < -\frac{\alpha}{\beta}
 $$
:::
